

\documentclass{article}

\usepackage{amsmath}
\usepackage{graphicx}


\author{Qing Scholten, Wessel van Sommeren}
\title{Controlling a rabbit plaque}

\begin{document}

\maketitle
\newpage
\tableofcontents
\newpage

\section{Introduction}
In 1859 the First Fleet of settlers arrived in Australia, with them Thomas Austin. Thomas Austin took 13 European rabbits with him on his journey, so that once in Australia he could set them free so that he could hunt them for food. What Thomas Austin did not know was that these European rabbits did not have any natural predators or competition in australia. So by 1920 the small population of 13 rabbits had turned into a rabbit plaque, in 1920 there were an estimated 10 billion rabbits in australia.In this paper we will attempt to model the rabbit plaque of australia by exploring the question "What is the most effective way to control a rabbit plaque comparing Hunting, Introducing a predator and Introducing a Competitor 



\section{Base case}
As Australia has about 7 616 666 square kilometer land and 1 371 000 square kilometer of this land is desert, one finds that about 7 479 566 square kilometer is fertile land. This follows from the assumption that every land outside the deserts is able to grow grass, which is the vegetation that is used in the model. Known is that "the average annual total herbage production at Moorepark for the period 2005–9 was 14 087 kg DM/ ha, with an average grass growth of 50·3 kg DM/ha/day." A 1 hectare is equal to 0.01 square kilometer, the avarage annual total herbage production 140.87 kg Dm/km^2, so for Australia this is about 1 052 646 462 kg Dm. This means that the amount of grass, as grass has about 17% dry material, is about 6 197 920 367 kg grass for the whole of Australia. As rabbits eat around 1 cup of grass for 2 lbs of body weight, this would convert to about 0.25 kilo gram grass for a medium sized rabbit of 2 kilo gram. This means that Australia has enough grass to house 12 395 840 734 rabbits without running out of food.
http://www.ga.gov.au/scientific-topics/national-location-information/landforms/deserts
https://hal.archives-ouvertes.fr/hal-01210354/document
https://www.teagasc.ie/media/website/animals/dairy/Whats_in_Grass_Todays_Farm_May2014.pdf
https://rabbit.org/suggested-vegetables-and-fruits-for-a-rabbit-diet/#:~:text=The%20bulk%20of%20fresh%20foods,for%20a%20rabbit%20to%20consume.&text=t%20to%20feed%20would%20be,into%20multiple%20feedings%20a%20day.

\section{Shooting rabbits}

\section{Importing foxes as natural preditors}
In the model that imports a natural preditor for the rabbits, foxes are used. Red foxes  eat around 500 grams of food per day. This means that, with rabbits that are roughly 2 kilo gram, a fox eats 0.25 rabbits per day, assuming they don't have any other food source. Assuming that foxes don't take away any food that the rabbits eat, the amount of foxes that Australia can house is directly depend directly on the amount of rabbits there are. As the gestation time of a red fox is 51 days and the litter size is on avarage 5 pups, we find that every day 5/(51*2) foxes are born per fox.
https://www.wildlifeonline.me.uk/animals/article/red-fox-diet-how-much-food#:~:text=Again%2C%20this%20is%20a%20deceptively,pound)%20of%20food%20per%20day.
https://ofnc.ca/programs/fletcher-wildlife-garden/flora-and-fauna-at-the-fwg/red-foxes-at-the-fwg

\section{Importing goats as natural competitors}
In the model that uses a rival for food for the rabbits, goats are used. As goats eat around 1 to 2 kilo gram hay daily, they would need to eat around 6 to 12 kilo gram grass per day, as grass is about 17% dry material and hay is mostly dry matter. Using the 9 kilo gram grass per day per goat in the models, means that Australia has enough grass to house 688 657 818 goats without running out of food. This means that for one goat housed within Australia, twelve rabbits less can be housed and that for every twelve rabbits, one less goat can be housed. As the gestation time for goats is between 145 and 155 days (taking the average 150 days) and about two goats per litter, the birth rate for the goats is 2/(150*2) per goat per day. Goats llive up to around 11 or 12 years, or 4015 to 4380. This means that the deathrate is on average 1/4197.5 goat per day.
smallholderfeed.co.uk/goat-feeding-guide/#:~:text=Hay%20or%20roughage%20should%20form,kg%20of%20hay%20per%20day.
https://www.teagasc.ie/media/website/animals/dairy/Whats_in_Grass_Todays_Farm_May2014.pdf
https://animals.mom.com/how-many-kids-do-goats-have-7907049.html
https://backyardgoats.iamcountryside.com/health/how-long-do-goats-live/

\end{document}
